paper1_results_figs_slimmed_50

### 2016-03-30 paper1_results_figs_slimmed_50.Rmd
tweaks

  #in main paper I want to just display sequential and mixture strategies
  strategies <- strategies[-1:-2]

@@

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             ggtitle(paste(strategy)) +
             xlab(NULL) 
  }

  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))

>>>>

  #in main paper I want to just display sequential and mixture strategies
  strategies <- c("Sequential", "Mix adaptive", "Mix both")
  strat_name <- c("Seq both","Adaptive both","Mix both")

@@

    plotlist[[strategy_num]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             ggtitle(paste(strat_name[strategy_num])) +
             xlab(NULL) 
  }

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.8))
